### 2016-01-26 src/4_OnlineLearning.tex
error in formulas OLS

\begin{equation*}
\label{eq:proyectorsol}
\mathbf{X \hat{\mathbf{X}} = PY} 
\end{equation*}

@@

\begin{eqnarray*}
\mathbf{X \hat{\mathbf{X}}} &=& \mathbf{PB} \\
\mathbf{U_1 \Sigma_1 V_1^\top \hat{\mathbf{X}}} &=& \mathbf{U_1 U_1^\top B} \\
\mathbf{ V_1^\top \hat{\mathbf{X}}} &=&  \mathbf{\Sigma_1^{-1} U_1^\top B} \\ 
\mathbf{ V_1^\top V_1 \mathbf{X}_1} &=& \mathbf{\Sigma_1^{-1}
U_1^\top B} \\
\mathbf{\mathbf{X}_1}&=& \mathbf{\Sigma_1^{-1} U_1^\top B}
\end{eqnarray*}

@@

\begin{eqnarray*}
\mathbf{\hat{\mathbf{X}}} &=& \mathbf{V_1 \mathbf{X}_1} \\
                &=& \mathbf{V_1 \Sigma_1^{-1} U_1^\top Y} \\
\mathbf{X^+} &=& \mathbf{V_1 \Sigma_1^{-1} U_1^\top} \, .
\end{eqnarray*}

@@

\subsection{Efficient computation}

In order to solve OLS in a efficient way, Coleman and
Sun~\cite{coleman+sun2010} presented an iterative algorithm which
uses $\mathbf{X}(\lambda)$ to approximate $\mathbf{X}(0)$.

>>>>

\begin{equation*}
\label{eq:proyectorsol}
\mathbf{A \hat{\mathbf{X}} = PY} 
\end{equation*}

@@

\begin{eqnarray*}
\mathbf{A \hat{\mathbf{X}}} &=& \mathbf{PY} \\
\mathbf{U_1 \Sigma_1 V_1^\top \hat{\mathbf{X}}} &=& \mathbf{U_1 U_1^\top Y} \\
\mathbf{ V_1^\top \hat{\mathbf{X}}} &=&  \mathbf{\Sigma_1^{-1} U_1^\top Y} \\ 
\mathbf{ V_1^\top V_1 \mathbf{X}_1} &=& \mathbf{\Sigma_1^{-1}
U_1^\top Y} \\
\mathbf{\mathbf{X}_1}&=& \mathbf{\Sigma_1^{-1} U_1^\top Y}
\end{eqnarray*}

@@

\begin{eqnarray*}
\mathbf{\hat{\mathbf{X}}} &=& \mathbf{V_1 \mathbf{X}_1} \\
                &=& \mathbf{V_1 \Sigma_1^{-1} U_1^\top Y} \\
\mathbf{A^+} &=& \mathbf{V_1 \Sigma_1^{-1} U_1^\top} \, .
\end{eqnarray*}

@@

\subsection{Efficient computation}
In regression problems we always require getting a matrix inverse which is
computationally expensive. However, in stream data problems the is a way to
obtain a matrix inverse approximation using the Sherman-Morrison-Woodbury. This
formula allows to get the inverse of a
the matrix $\mathbf{A+uv^\top}$ if we already calculated the
inverse of $\mathbf{A}$ as follows:

\begin{equation}
\label{eq:SMW}
(\mathbf{A+uv^\top})^{-1}=\mathbf{A}^{-1}-
\frac{\mathbf{A^{-1}uv^\top A^{-1}}}{\mathbf{1+v^\top A^{-1}u}}
\end{equation}

Alternatively, Coleman and
Sun~\cite{coleman+sun2010} presented an iterative algorithm which
uses $\mathbf{X}(\lambda)$ to approximate $\mathbf{X}(0)$.
